---
title: "Home Work 3 DDS 6306"
author: "Ayoade Dare"
date: "February 13, 2019"
output:
  html_document: default
  pdf_document: default
---

Git Code

ayoad@DESKTOP-L2HC7DU  ~/Documents (master)

$ pwd

/c/Users/ayoad/Documents

ayoad@DESKTOP-L2HC7DU  ~/Documents (master)

$ cd /D/OneDrive/Documents/SMU-DESKTOP-l2HC7DU/Classes/"MSDS 6306 Doing D
atascience"/"Unit 3"/

ayoad@DESKTOP-L2HC7DU  /D/OneDrive/Documents/SMU-DESKTOP-l2HC7DU/Classes/M
SDS 6306 Doing Datascience/Unit 3

$ pwd

/D/OneDrive/Documents/SMU-DESKTOP-l2HC7DU/Classes/MSDS 6306 Doing Datascie
nce/Unit 3

ayoad@DESKTOP-L2HC7DU MINGW64 /D/OneDrive/Documents/SMU-DESKTOP-L2HC7DU/Classes/MSDS 6306 Doing Datascience/Unit 3

$ git clone https://github.com/awesomedata/awesome-public-datasets.git
2a.
```{r Import Titanic csv, echo=TRUE}
df<-read.csv("D:/OneDrive/Documents/SMU-DESKTOP-L2HC7DU/Classes/MSDS 6306 Doing Datascience/Unit 3/awesome-public-datasets/Datasets/titanic.csv",sep =",",header = TRUE,stringsAsFactors = FALSE)
```

2b.
```{r Gender Count}
library(plyr)
gender<-count(df,vars = "Sex")

```

```{r Gender, echo=TRUE}
View(gender)
```
Plot of the genders on the Titanic
```{r Plot, echo=FALSE}
library(ggplot2)
ggplot(data = gender,aes(gender$Sex,gender$freq))+geom_bar(stat = "identity",width = 0.5,fill="blue")+ggtitle("Gender Count of the passengers on the Titanic")+xlab("Gender") +ylab("Frequency")
```

2c.


3.

```{r Import Sleep Data, echo=TRUE}
sleep_data<-read.csv("D:/OneDrive/Documents/SMU-DESKTOP-L2HC7DU/Classes/MSDS 6306 Doing Datascience/Unit 3/HW3/sleep_data_01.csv",sep = ",",header = TRUE,stringsAsFactors = FALSE)
```




3a-3d
```{r Sleep Function}
Sleep_Function<-function(x){
  Age_Median<-median(x[["Age"]],na.rm = TRUE)
  Sleep_Min<-min(x[["Duration"]],na.rm = TRUE)
  Sleep_Max<-max(x[["Duration"]],na.rm = TRUE)
  Sleep_Mean<-mean(x[["RSES"]],na.rm = TRUE)
  Sleep_sd<-sd(x[["RSES"]],na.rm = TRUE)
  sleep_range<-Sleep_Max-Sleep_Min
  Report<-c(Age_Median/5,Sleep_Mean/5,Sleep_sd/5,sleep_range)
  names(Report)<-c("MedianAge","SelfEsteem","SE_SD","Duration Range")
  round(Report,2)
}
Sleep_Function(sleep_data)
```

3e.
#```{r Sleep Function, echo=TRUE}
#Sleep_Function(sleep_data)
#```

4 a-c
```{r}
library(fivethirtyeight)
df<-fivethirtyeight::college_recent_grads
vignette("fivethirtyeight",package = "fivethirtyeight")

```

4d
```{r echo=TRUE}
dim(df)

```

```{r echo=TRUE}
colnames(df)

```

```{r echo=TRUE}
str(df)
```

5.
```{r}
colnames(df)
NCOL(df)
```

```{r}
library(plyr)
major_count<-count(df,vars = "major_category")
major_count
```

```{r}
library(ggplot2)
par(las=2)
mj_plot<-ggplot2::ggplot(major_count,aes(major_count$major_category,major_count$freq))+geom_bar(stat = "identity",fill="red")+ggtitle("Popular Major")+xlab("Major Categories")+ylab("Frequency")
mj_plot +coord_flip()
```

5d.
```{r}
write.csv(df,file = "FiveThirtyEight.csv",row.names = FALSE)
```

